A fast unified model for parsing and sentence understanding

### 2016-03-18 writing/hard_stack_paper/paper.tex
Tighten up intro prose

Of these, the TreeRNN is the principled choice, since meaning in natural language sentences is constructed incrementally according to a tree structure \citep[][i.a.]{Szabolcsi:2009}. However, while these models have shown promise \citep{tai2015improved,li2015tree,bowman2015trees}, they have largely been overlooked in favor of sequence-based RNNs because of their incompatibility with batched computation and their reliance on external parsers.  Batched computation---performing synchronized computation across many examples at once---yields order-of-magnitude improvements in model run time, and is a crucial enabling technology in allowing neural networks to be trained efficiently on large datasets. Because TreeRNNs use a different model structure for each sentence, batched computation is impossible in standard implementations. In addition, standard TreeRNN models can only operate on sentences that have already been processed by a syntactic parser, which slows and complicates the use of these models at test time for most applications.

>>>>

Of these, the TreeRNN is the principled choice, since meaning in natural language sentences is constructed incrementally according to a tree structure \citep[][i.a.]{Szabolcsi:2009}. TreeRNNs have shown some promise \citep{tai2015improved,li2015tree,bowman2015trees}, but have largely been overlooked in favor of sequence-based RNNs because of their incompatibility with batched computation and their reliance on external parsers.  Batched computation---performing synchronized computation across many examples at once---yields order-of-magnitude improvements in model run time, and is a crucial enabling technology in allowing neural networks to be trained efficiently on large datasets. Because TreeRNNs use a different model structure for each sentence, batched computation is impossible in standard implementations. In addition, standard TreeRNN models can only operate on sentences that have already been processed by a syntactic parser, which slows and complicates the use of these models at test time for most applications.
